\bf Landslide: Systematic Testing in 15-410 \\ User Guide and Survey

### 2015-01-16 irb/survey.tex
update irb forms slightly

Normally here I would write something researchy about systematic testing and preemption points, but if you're here it probably means you know what this is about. If you don't, please refer to the lecture material.
\\

\noindent Thanks for volunteering to try out Landslide. We have worked hard to make it nice enough to give to you, and we hope you're just as excited as we are to try out some systematic testing techniques the world has never seen before.
\\

\noindent You should have received a document titled {\em User Study Information Sheet} that describes your rights as a study participant and our confidentiality procedures. If you are missing this, please contact Ben immediately at {\tt bblum@cs.cmu.edu}.
% TODO: Host them on maxi or contrib and link to them.

>>>>

%Normally here I would write something researchy about systematic testing and preemption points, but if you're here it probably means you know what this is about. If you don't, please refer to the lecture material.
%\noindent
Thanks for volunteering to try out Landslide. We have worked hard to make it nice enough to give to you, and we hope you're just as excited as we are to try out some systematic testing techniques the world has never seen before.
\\

\noindent You should have received a document titled {\em User Study Information Sheet} that describes your rights as a study participant and our confidentiality procedures. If you are missing this, please contact Ben immediately at {\tt bblum@cs.cmu.edu}. If you have not yet reviewed the lecture slides (found on the course website), please do so before proceeding.
% TODO: Host them on maxi or contrib and link to them.
